\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PhD Notes}
\author{Robert Twyman}
\date{October 2018}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle
This list has been moved to OneNote


\section{To-do List}

\begin{itemize}
\item Read the 5 documents Kris sent me in the reading list email package
\item 
\item Read-up on ill-conditioned problems
\item Fourier transforms revision
\item Look into Portico (FOR????)
\end{itemize}

\begin{itemize}
\item See why mac messages say they they are undelivered  
\end{itemize}






\begin{itemize}
\item Maybe (if time permits) write up the initial notes from the meeting with Kris
\end{itemize}

\section{Budget}
Aside from your stipend (covering 3.5 years) and fees (covering 3 years), each of you has a budget as follows
 
£8000 Travel
\begin{itemize}
\item Travel will include trips to four (4) international conferences, T\&S and conference fees estimated at £1500 per conference. Travel is specifically for presentation (abstract, posters, scientific talks) related to ongoing research. Travel will be booked in coordination with GE travel policies. Supported travel expenses not to exceed the amount listed above.
\item Travel will include an approximate one (1) month visit to GE Healthcare and/or GE Research Center, estimated at £2000 per visit. Travel to GE sites is for purpose of advancing ongoing research. Travel will be booked in coordination with GE travel policies. Supported travel expenses not to exceed the amount listed above.
\item £2100 Equipment includes high-end laptop for use on related research.
\item £500 training fees (for relevant external courses to advance knowledge as it applies to relevant research)
\item £3500 cluster computing costs
\end{itemize}




\section{PC/laptop selection}

\begin{itemize}
\item Have use of UCL clusters
\item have a macbook (macOS)
\item have a home PC (windows)
\item 
\item 
\item 
\item need something portable - lightweight is ideal 
\item 	Something for conferences
\item Need something powerful- something I can "hook-up" to monitors at INM
\item need something secure, cant use my own mac unless encrypted?? 
\end{itemize}

It has to be a laptop,

A Desktop is not portable - so I could never work on GE stuff anywhere else - ?do I need to work on GE stuff anywhere else? I would have access to it on the UCL cluster??

Do i wait and see? 
 but how would I learn GE stuff
Give it thought

There are three levels: 
portability(less power)     					macbook(unsecured)		Could buy a newone but mine is not dead yet
medium power (non-portable)			   Desktop							  
Superpower (difficult to use)               Cluster



\bibliographystyle{plain}
\bibliography{Reading List}
\end{document}
